Do moral communities have a spatial dimension? A spatial exploratory analysis of places of worship and violent crime in the city of Recife, Brazil

### 2019-10-17 Moral_Communities_and_Crime_v1.tex
Knitted the pdf file with the text again to remove the fictitious author names that the editorial assistant did not find amusing.

\author{  Aye B. Cee \and  Dee E. Eff \and  Gee H. Eye \and  Jay K. Elle \and  }

\institute{
        Aye B. Cee \at
     A Department, University of XXX \\
     \email{\href{mailto:abc@example.edu}{\nolinkurl{abc@example.edu}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Dee E. Eff \at
     A Department, University of XXX \\
     \email{\href{mailto:def@example.edu}{\nolinkurl{def@example.edu}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Gee H. Eye \at
     A Department, University of XXX \\
     \email{\href{mailto:ghi@example.edu}{\nolinkurl{ghi@example.edu}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Jay K. Elle \at
     Some School, University of WWW \\
     \email{\href{mailto:jkl@school.edu}{\nolinkurl{jkl@school.edu}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }

>>>>

\author{  Author One \and  Author Two \and  Author Three \and  Author Four \and  }

\institute{
        Author One \at
     A Department, University of XXX \\
     \email{\href{mailto:abc@example.edu}{\nolinkurl{abc@example.edu}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Author Two \at
     A Department, University of XXX \\
     \email{\href{mailto:def@example.edu}{\nolinkurl{def@example.edu}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Author Three \at
     A Department, University of XXX \\
     \email{\href{mailto:ghi@example.edu}{\nolinkurl{ghi@example.edu}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
        Author Four \at
     Some School, University of WWW \\
     \email{\href{mailto:jkl@school.edu}{\nolinkurl{jkl@school.edu}}}  %  \\
%             \emph{Present address:} of F. Author  %  if needed
    \and
    }
